The \dealii{} Library, Version 9.3

### 2021-06-18 9.3/paper.tex
Update 9.3/paper.tex
Co-authored-by: Timo Heister <timo.heister@gmail.com>

The requirement to download, compile and install \dealii{} and its dependencies from
source is of major interest for many \dealii{}-users.
%
This can be of importance on arbitrary Linux-based operating systems for which
binary packages aren't available or on compute clusters and other machines
without root privileges for the user to install system dependencies.

@@

\candi is a bash-script based tool, it is the abbreviation of ``compile and install''
and it is released under the GNU LGPL v3.0.
%
The origin of \candi{} is a fork made in 2013 from \texttt{dorsal},
a retired source based installer for the \texttt{FEniCS} library.
%
The \candi{} tool can be found via the download page of \dealii{} since version 8.5
and is under active maintenance.
To install older releases of \dealii{} toolchains one can checkout the branch
corresponding to the \dealii{}-version with \texttt{git}.

>>>>

The requirement to download, compile and install \dealii{} and its dependencies from
source is of major interest for many \dealii{}-users.
%
Compiling dependencies from source can be of importance on arbitrary Linux-based operating systems for which
binary packages aren't available or on compute clusters and other machines
without root privileges for the user to install system dependencies.

@@

\candi is a bash-script based tool, it is the abbreviation of ``compile and install''
and it is released under the GNU LGPL v3.0.
%
The origin of \candi{} is a fork made in 2013 from \texttt{dorsal},
a retired source based installer for the \texttt{FEniCS} library.
%
The \candi{} tool can be found via the download page of \dealii{} since version 8.5
or from github.com/dealii/candi and is under active development.
To install older releases of \dealii{} toolchains one can checkout the branch
corresponding to the \dealii{}-version with \texttt{git}.
